Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-02-22 manuscript/manuscript.Rmd
Update manuscript.Rmd

>>>>

```{r shifted-distributions-other-criteria, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Shift-sensitive power transformation produces transformation parameters that are invariant to location. ",
  "Samples were drawn from normal, right-skewed and left-skewed distributions, respectively,  which then underwent a shift $d$. ",
  "Estimates of transformation parameter $\\lambda$ with the original power transformations (circle) show strong dependency on the overall location of the distribution, ",
  "whereas estimates with the shift-sensitive power transformations (triangle) are constant.")

  p <- ggplot2::ggplot(
    data = data,
    mapping = ggplot2::aes(
      x = d,
      y = lambda,
      colour = estimation_method))
  p <- p + plot_theme
  p <- p + ggplot2::geom_point()
  p <- p + ggplot2::scale_x_continuous(
    name = latex2exp::TeX("$d$"),
    labels = scales::math_format())
  p <- p + ggplot2::scale_y_continuous(
    name = latex2exp::TeX("$\\lambda$"),
    limits = limits)
  p <- p + ggplot2::theme(
    plot.title=ggplot2::element_text(
      hjust=0.5,
      size=ggplot2::rel(1.0)))

  if(guide){
    p <- p + paletteer::scale_color_paletteer_d(
      palette = "ggthemes::Tableau_10",
      drop = FALSE)
    p <- p + guides(colour = ggplot2::guide_legend(title = "Optimisation criterion"))

  } else {
    p <- p + paletteer::scale_color_paletteer_d(
      palette = "ggthemes::Tableau_10",
      drop = FALSE,
      guide = "none")
  }

if(!file.exists(file.path(manuscript_dir, "shifted_distributions_plot.RDS"))){
  stop("Data are missing for creating shifted-distribution plots.")

# Update distribution, method and version to factors.
data$distribution <- factor(
  x = data$distribution,
  levels = c("normal", "right-skewed", "left-skewed"))
data$method <- factor(
  x = data$method,
  levels = c("box_cox", "yeo_johnson"),
  labels = c("Box-Cox", "Yeo-Johnson"))
data$version <- factor(
  x = data$version,
  levels = c("original", "shift-sensitive"))
data$estimation_method <- factor(
  x = data$estimation_method,
  levels = c("mle", "anderson_darling", "cramer_von_mises", "jarque_bera", "dagostino"),
  labels = c("MLE", "Anderson-Darling", "Cramér-von Mises", "Jarque-Bera", "D'Agostino")
)

#### Normal distribution -------------------------------------------------------

# Box-Cox-original
p_bc_normal <- .create_lambda_shift_plot(
  data = data[distribution == "normal" & method == "Box-Cox" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-20.0, 35.0))
p_bc_normal <- p_bc_normal + ggplot2::ggtitle(label="normal distribution")

# Yeo-Johnson
p_yj_normal <- .create_lambda_shift_plot(
  data=data[distribution == "normal" & method == "Yeo-Johnson" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-20.0, 35.0))

# Box-Cox
p_bc_right <- .create_lambda_shift_plot(
  data = data[distribution == "right-skewed" & method == "Box-Cox" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-15.0, 1.0))
p_bc_right <- p_bc_right + ggplot2::ggtitle(label="right-skewed distribution")

# Yeo-Johnson
p_yj_right <- .create_lambda_shift_plot(
  data = data[distribution == "right-skewed" & method == "Yeo-Johnson" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-15.0, 1.0))

# Box-Cox
p_bc_left <- .create_lambda_shift_plot(
  data = data[distribution == "left-skewed" & method == "Box-Cox" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-50.0, 60.0),
  guide = TRUE)
p_bc_left <- p_bc_left + ggplot2::ggtitle(label="left-skewed distribution")

# Yeo-Johnson
p_yj_left <- .create_lambda_shift_plot(
  data = data[distribution == "left-skewed" & method == "Yeo-Johnson" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-50.0, 60.0))

p <- egg::ggarrange(
  plots=list(
    p_bc_normal, p_yj_normal,
    p_bc_right, p_yj_right,
    p_bc_left, p_yj_left),
  ncol=3,
  heights=c(1.0, 1.0),
  byrow=FALSE,
  draw=FALSE)
p

p <- ggplot2::ggplot(
  data = data,
  mapping = ggplot2::aes(
    x = d,
    y = lambda,
    colour = estimation_method))
p <- p + plot_theme
p <- p + ggplot2::geom_point()
p <- p + ggplot2::scale_x_continuous(
  name = latex2exp::TeX("$d$"),
  labels = scales::math_format())
p <- p + ggplot2::scale_y_continuous(
  name = latex2exp::TeX("$\\lambda$"))
p <- p + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE)
p <- p + guides(colour = ggplot2::guide_legend(title = "optimisation criterion"))

p <- p + ggplot2::facet_grid(
  method + version ~ distribution,
  scales = "free")
